Are We Reusing Outdated and License-violating Code \newline from Stack Overflow?

### 2017-01-31 cloneoverflow-latex/cloneoverflow.tex
Improved the diagram and text

In this study, we treat code snippets that are copied from software systems to Stack Overflow, and vice versa, as code clones. We call them \textbf{online code clones} (or sometimes only call \textbf{clones} for brevity). There are four ways to create online code clones: (1) code is cloned from a software project to Stack Overflow as an example; (2) code is cloned from Stack Overflow to a software project to obtain a functionality, perform a particular task, or fixing a bug; (3) code is implicitly cloned from one software project to another by having Stack Overflow as a medium; and (4) code is cloned from an external source to both a software project and Stack Overflow. \textbf{Online code clones can similarly lead to a problem of outdated code, bug propagation, licensing violation, and software vulnerability as classical code clones.} Unfortunately, they are more difficult to locate and fix since the search space in online code corpora is larger and no longer confined in a local repository.

@@

A motivating example of outdated code in online code clones can be found in the a Stack Overflow post regarding how to implement \textit{RawComparator} in Hadoop\footnote{http://stackoverflow.com/questions/22262310}. In \Cref{fig:before-after}, the left hand side shows a code snippet embedded as a part of accepted answer to the question. The snippet shows how Hadoop implements \textit{compare} method in its \textit{WritableComparator} class. The code snippet on the right hand side shows another version of the same \textit{compare} method in \textit{WritableComparator} class but it is extracted from the latest version of Hadoop. We can obviously see that they are highly similar except one line, \verb|buffer.reset(null,0,0);|, is added in the latest version after \verb|key2.readFields(buffer);|. The added line is intended for cleaning up the reference in \verb|buffer| variable. While this change has already been introduced into \textit{compare} method in the latest version of Hadoop, the code example in Stack Overflow post is still unchanged. This example shows that there can be inconsistencies between online code clones and its original. The code snippet on Stack Overflow can be outdated.  %Since reusing source code from Stack Overflow is considered a common practice nowadays, the scale of online code cloning is more than intra or inter project clone in a local code bases. 
%This is an emerging and challenging problem. Since studies in this area are still limited, we aim to gain more insight of the problem in this study. %We are interested to gain more insights of online code clone in this study.

@@

\vspace{0.5ex}%
\noindent\textbf{1.~A manual study of online code clones:} 
We used two clone detection tools to discover 270,429,422 similar code snippet pairs and manually investigated 3,450 candidate clone pairs between Java code snippets obtained from Stack Overflow accepted answers and 111 Java open source projects.

\vspace{0.5ex}%
\noindent\textbf{2.~Addressing the problems of reusing source code between open source projects and Stack Overflow:} Our study shows that there are at least 523 clones that have been obviously copied from open source projects or external online sources to Stack Overflow as code examples which potentially violate their software licenses. Importantly, 53 out of the 96 online code clones on Stack Overflow are outdated and questionable for being reused.

\vspace{0.5ex}%
\noindent\textbf{3.~Online code clone oracle:} The 3,450 manually investigated and validated online clone pairs are available for download on the study website\footnote{https://some.where} and can be used as a clone oracle.

@@

\textbf{Open source systems}: we selected an established corpus for an empirical software engineering study called \textbf{Qualitas} \cite{QualitasCorpus} for this study. It is a curated Java corpus that has been used in several software engineering studies \cite{Taube-Schock2011,Beckman2011,Vasilescu2011,Omar2012}. The projects in the corpus represent various domains of software systems ranging from programming language to 3D and visualisation \cite{QualitasCorpus}. We selected the 20130901r release of Qualitas corpus containing 112 Java open source projects. This release contains projects with releases no later than 1st September 2013. We chose a snapshot late back in 2013 since we are interested in online code clones in the direction from open source projects to Stack Overflow. The 20130901r snapshot provides Java code that is at least 3 years old from the time of the experiment (January to December 2016). The time difference is sufficiently long for a number of code snippets to be copied onto Stack Overflow. Out of 112 Qualitas projects, there is one project, \textit{jre}, that does not contain Java source code due to its licensing limitation \cite{QualitasCorpus} so it is removed from the study. This resulted in total of 111 projects analysed in the study. As shown in \Cref{tab:datasets}, the 111 Qualitas project have 160,937 Java files containing 19,086,883 lines of code. %Details of the 109 Qualitas projects and their licenses are listed in Table \ref{t:new_and_old}.

@@

\begin{table}
	\centering
	\caption{Statistics of clones found between Stack Overflow and Qualitas projects using Simian (\textit{S}) and NiCad (\textit{N}) with default (\textit{D}) and EvaClone (\textit{E}) configurations}
	\label{tab:raw_stats}
	\small
	\resizebox{\columnwidth}{!}{%
		\begin{tabular}{l|r|r|r|r}
			\hline
			Stats & \multicolumn{1}{c|}{$S_D$} & \multicolumn{1}{c|}{$S_E$} & \multicolumn{1}{c|}{$N_D$} & \multicolumn{1}{c}{$N_E$} \\
			\hline
			Snippets & 1,086 & 1,531 & 1,392 & 12,886 \\
			Total C$_{\textrm{\textit{pairs}}}$ & 67,570 & 63,635,844 & 632,855 & 251,449,849 \\
			Avg.~C$_{\textrm{\textit{pairs}}}$ & 62 & 41,565 & 455 & 19,356 \\
			Avg.~C$_{\textrm{\textit{size}}}$ & 7.72 & 4.79 & 9.84 & 5.33 \\
			Avg.~C$_{\textrm{\textit{\%}}}$ & 29\% & 28\% & 25\% & 21\% \\
			\hline
		\end{tabular} %
	}
\end{table}

@@

Agreed clone pairs are clone pairs that pass Bellon's good- or ok-match criteria and selected for manual investigation. Similar to the original study, we select a threshold \textit{p} of 0.7 for both \textit{good} and \textit{ok} pairs \cite{Bellon2007}. %The number of projects processed by the clone detection tools are listed in \Cref{tab:projects_missing}. 
We encountered NiCad failures with a few Qualitas projects.~$N_D$ could not detect clones in Hibernate due to clustering errors. $N_E$ generated renaming errors for 5 projects including Vuze, Hibernate, Myfaces, Netbeans, and Spring. We had contacted the creator of NiCad regarding the issues. They identified them as problems of long file paths and TXL grammars which will be fixed in the next NiCad releases. As a result, we did not have NiCad clones from these projects in the agreed clone pairs. Simian clones of the same projects also disappeared from the agreed clone pairs since they could not find matches.

@@

\textbf{To answer RQ1, we found 32,039 clone candidates between 111 Qualitas projects and 144,075 Stack Overflow snippets. They are 2,308 \textit{good}, 11,749 \textit{ok}, 17,801 $S_D$, and 181 $N_D$ pairs. After classification, we found at least \FIXME{NUMBER} online code clones pairs that are clones between Stack Overflow and Qualitas.}

@@

\begin{table}
	\centering
	\caption{Seven patterns of online code cloning}
	\label{tab:classification_scheme}
	\resizebox{\columnwidth}{!}{%
		\begin{tabular}{|c|p{8.4cm}|}
			\hline 
			Patt. & Descriptions \\ 
			\hline 
			QS & Cloned from Qualitas project to Stack Overflow (Q $\rightarrow$ S). \\ 
			\hline 
			SQ &Cloned from Stack Overflow to Qualitas project (S $\rightarrow$ Q). \\ 
			\hline 
			UD & Cloned from each other or from an external source \textit{X} outside the project (unknown) (S $\leftrightarrow$ Q $\vee$ (X $\rightarrow$ S $\wedge$ X $\rightarrow$ Q)).
			\\ 
			\hline 
			ES & Cloned from an external source (X $\rightarrow$ S $\wedge$ X $\rightarrow$ Q).
			\\ 
			\hline 
			BP & Boiler-plate or IDE auto-generated
			\\ 
			\hline 
			IN & Inheritance, interface implementation 
			\\ 
			\hline 
			FC & Accidental similarity, false clones \\ 
			\hline 
		\end{tabular}  %
	}
\end{table}

@@

Nevertheless, we adopted one of Kapser's cloning patterns, boiler-plate code and API/library protocol as pattern BP. We then added 6 new patterns observed as common cloning patterns from our preliminary study. The seven patterns include QS, SQ, UN, ES, BP, IN, and FC as presented in \Cref{tab:classification_scheme}. QS (\textbf{Q}ualitas to \textbf{S}tack Overflow) represents clones that has evidence to be copied from Qualitas to Stack Overflow (by having comments in source code and explanation/links in Stack Overflow post). Pattern SQ (\textbf{S}tack Overflow to \textbf{Q}ualitas) is the opposite of QS. UD (\textbf{U}nknown \textbf{D}irection) is a cloning that is exactly identical or highly similar but without any attribution of copying. ES (\textbf{E}xternal \textbf{S}ources) is a cloning that has an evidence of copying from an external source(s). Pattern BP (\textbf{B}oiler-\textbf{P}late) represents clones containing boiler-plate code of \verb|equals()| methods, getters and setters, or IDE-generated code (e.g.~GUI components). Pattern IN (\textbf{In}heritance/Interface) is cloning because of inheritance of the same super class or implementation of the same interface. They usually share similar overriding methods. The last pattern, FC (\textbf{F}alse \textbf{C}lones), represents false clone pairs. They can be either accidentally similar clones (e.g.~similar \texttt{try-catch} statements), similar clones after code normalisation, or just false positives of the tools. Using the classification patterns, we can also calculate the number of true and false positives. We are looking for unique and meaningful clones in this study. Thus, we consider clone pairs classified into pattern QS, SQ, and UN as true positive, and BP, IN, and FC as false positive.

@@

@@

\Cref{fig:outdated} shows the findings of outdated online clones on Stack Overflow. The comparison with the clones' latest versions revealed that 55 clone pairs were outdated and they were all Stack Overflow accepted answers. Hadoop and Spring have the maximum number of 9 outdated code clones, followed by 6 from Tomcat, and 5 from Eclipse-SDK. An example of outdated code in hadoop's \textit{WritableComparator.java} is shown in \Cref{fig:before-after} as we discussed before. We also found a few outdated code which contained heavy modifications. For example, the code snippet in Stack Overflow post 23520731, a copy of \textit{SchemaUpdate.java} in Hibernate, it had been heavily modified in the latest version (as shown in \Cref{fig:hibernate_outdated_code}). Lastly, we found some ``orphan'' snippets. These snippets cannot find their originals in the latest version of the projects anymore. For example, the snippet in Stack Overflow post 3758110, a copy of \textit{DefaultAnnotationHandlerMapping.java} in Spring, was deleted in commit \texttt{02a4473c62d8240837bec297f0a1f3cb67ef8a7b} by Chris Beams on 20th January 2012 at 22:51:02, two years after it was posted. %The latest version of Spring does not contain the file anymore.

The outdated online code clones can cause problems ranging from uncompilable code due to different API usage to bug propagations. An outdated code with a subtle change (e.g.~\Cref{fig:before-after}) may be copied and reused without awareness from developers. Although Stack Overflow has a voting mechanism that may mitigate this outdated code issue, the check mark symbol in front of the accepted answer is still attractive to naive developers who are ignorant.
%Usually when developers reuse a code snippet from a Stack Overflow post and find that it does not work nor compatible with their environment. They can cast a down vote to that answer resulting in low votes for the answer (which might be outdated). However, if the answer is marked as accepted by the person who asks the question, the check mark symbol attached to the answer is still attractive to naive developers who are ignorant.

@@

	\begin{tabular}{r|l|p{4.5cm}|r|r|l|l|l|c|l}

@@

		No. & Project & File & Start & End & License & SO Post & License & $C$ & C$_{\textit{\textrm{date}}}$ \\

@@

			1 & aspectj-1.6.9  & aspectjtools/../Agent.java  & 7 & 18 & -- & 18303692 & -- & $M$  & 2015-09-08 \\
			2 & aspectj-1.6.9  & aspectjweaver/../Agent.java  & 7 & 18 & -- & 18303692 & & $M$  & 2015-09-08 \\
			3 & eclipse-SDK  & GenerateToStringAction.java  & 113 & 166 & EPLv1 & 2513183 & EPLv1 & $M$  &  2015-03-17 \\
			4 & eclipse-SDK  & GenerateToStringAction.java  & 117 & 126 & EPLv1  &  2513183	& EPLv1 & $M$  &  2015-03-17 \\
			5 & eclipse-SDK  & GenerateToStringAction.java  & 143 & 165 & EPLv1  &  2513183	& EPLv1 & $M$  &  2015-03-17 \\
			6 & eclipse-SDK  & GenerateToStringAction.java  & 178 & 187 & EPLv1  &  2513183	& EPLv1 & $M$  & 2011-03-01 \\
			7 & eclipse-SDK  & WizardDialog.java  & 377 & 394 & EPLv1  &   11861598	& -- & $M$  &  2011-02-03 \\
			8 & hadoop-1.0.0  & DBCountPageView.java  & 275 & 287 & Apache-2 & 21702608 & -- & $M$  & 2011-06-12 \\
			9 & hadoop-1.0.0  & DBCountPageView.java  & 289 & 309 & Apache-2 & 21702608 & -- & $M$  & 2011-06-12 \\
			10 & hadoop-1.0.0  & JobSubmissionFiles.java  & 46 & 55 & Apache-2 & 14845581 & -- & $M$  & 2012-06-25 \\
			11 & hadoop-1.0.0  & mapred/../LineRecordReader.java  & 47 & 60 & Apache-2 & 16180910 & -- & $M$  & 2011-07-25 \\
			12 & hadoop-1.0.0  & mapreduce/../LineRecordReader.java  & 75 & 99 & Apache-2 & 16180910 & -- & $M$  & 2011-07-25 \\
			13 & hadoop-1.0.0  & StringUtils.java  & 40 & 56 & Apache-2 & 801987 & -- & $M$  & 2013-02-04 \\
			14 & hadoop-1.0.0  & TestJobCounters.java  & 186 & 192 & Apache-2 & 18833798 & -- & $M$  & 2011-06-12 \\
			15 & hadoop-1.0.0  & TextOutputFormat.java  & 75 & 99 & Apache-2 & 16928749 & -- & $M$  & 2011-06-12 \\
			16 & hadoop-1.0.0  & WritableComparator.java  & 44 & 54 & Apache-2 & 22315734 & -- & $M$  & 2014-11-20 \\
			17 & hibernate-4.2.2  & ConnectionProviderInitiator.java  & 65 & 93 & -- & 15168494 & -- & $M$  & 2012-06-24 \\
			18 & hibernate-4.2.2  & Example.java  & 224 & 243 & -- & 24924255 & -- & $M$  & 2013-04-23 \\
			19 & hibernate-4.2.2  & SchemaUpdate.java  & 115 & 168 & -- & 23520731 & -- & $M$  & 2016-02-05 \\
			20 & hibernate-4.2.2  & SettingsFactory.java  & 244 & 255 & -- & 8257554 & -- & $D$  & 2011-03-11 \\
			21 & hibernate-4.2.2  & SQLServer2005LimitHandler.java  & 43 & 61 & -- & 23967852 & -- & $M$  & 2015-03-12 \\
			22 & jasperreports-3.7.4  & JRVerifier.java  & 982 & 998 & LGPLv3+ & 8037824 & -- & $M$  & 2008-04-17 \\
			23 & jasperreports-3.7.4  & JRVerifier.java  & 1221 & 1240 & LGPLv3+ & 8037824 & -- & $M$  & 2011-05-20 \\
			24 & jfreechart-1.0.13  & AbstractXYItemRenderer.java  & 532 & 569 & LGPLv2.1+ & 12936580 & -- & $M$  & 2016-02-19 \\
			25 & jfreechart-1.0.13  & KeyToGroupMap.java  & 18 & 30 & LGPLv2.1+ & 16058183 & -- & $M$  & 2013-07-03 \\
			26 & jfreechart-1.0.13  & SpiderWebPlot.java  & 502 & 520 & LGPLv2.1+ & 21998949 & -- & $M$  & 2008-06-02 \\
			27 & jfreechart-1.0.13  & SpiderWebPlot.java  & 522 & 536 & LGPLv2.1+ & 21998949 & -- & $M$  & 2008-06-02 \\
			28 & jgraph-5.13.0.0  & HelloWorld.java  & 16 & 22 & LGPLv2.1+ & 6722760 & -- & $R$  & 2014-04-13 \\
			29 & jgraph-5.13.0.0  & HelloWorld.java  & 28 & 40 & LGPLv2.1+ & 6722760 & -- & $R$  & 2014-04-13 \\
			30 & jgraph-5.13.0.0  & HelloWorld.java  & 31 & 36 & LGPLv2.1+ & 6722760 & -- & $R$  & 2014-04-13 \\
			31 & jgraph-5.13.0.0  & HelloWorld.java  & 39 & 56 & LGPLv2.1+ & 6722760 & -- & $R$  & 2014-04-13 \\
			32 & jstock-1.0.7c  & GoogleMail.java  & 18 & 42 & GPLv2+ & 14940863 & -- & $M$  & 2015-12-13 \\
			33 & jstock-1.0.7c  & GoogleMail.java  & 18 & 42 & GPLv2+ & 24680923 & -- & $M$  & 2015-12-13 \\
			34 & jung2-2\_0\_1  & ShortestPathDemo.java  & 106 & 117 & -- & 6025026 & -- & $M$  & 2010-04-13 \\
			35 & jung2-2\_0\_1  & ShortestPathDemo.java  & 158 & 172 & -- & 6025026 & -- & $M$  & 2010-04-13 \\
			36 & junit-4  & Assert.java  & 33 & 52 & -- & 23586872 & -- & $M$  & 2015-05-12 \\
			37 & junit-4  & ExternalResource.java  & 4 & 23 & -- & 7504040 & -- & $M$  & 2016-06-25 \\
			38 & junit-4.11  & ExpectException.java  & 11 & 29 & -- & 8802082 & -- & $M$  & 2014-05-26 \\
			39 & poi-3.6  & WorkbookFactory.java  & 18 & 28 & Apache-2 & 12593810 & -- & $M$  & 2015-04-29 \\

>>>>

We call code snippets that are copied from software systems to online Q\&A websites (such as Stack Overflow), and vice versa as ``online code clones'' (sometimes only ``clones'' for brevity). There are four ways to create online code clones: (1) code is cloned from a software project to a Q\&A website as an example; (2) code is cloned from a Q\&A website to a software project to obtain a functionality, perform a particular task, or fixing a bug; (3) code is implicitly cloned from one software project to another by having a Q\&A website as a medium; and (4) code is cloned from an external source to both a software project and a Q\&A website. Online code clones can similarly lead to a problem of outdated code, bug propagation, licensing violation, and software vulnerability as classical code clones. Unfortunately, they are more difficult to locate and fix since the search space in online code corpora is larger and no longer confined in a local repository.

In this study, we are interested in locating online code clones on Stack Overflow that are cloned from open source projects and study them on two aspects: obsoleteness and licensing issues.

@@

A motivating example of outdated online code clones can be found in the a Stack Overflow post regarding how to implement \textit{RawComparator} in \texttt{hadoop}\footnote{http://stackoverflow.com/questions/22262310}. In \Cref{fig:before-after}, the left hand side shows a code snippet embedded as a part of accepted answer to the question. The snippet shows how \texttt{hadoop} implements \textit{compare} method in its \textit{WritableComparator} class. The code snippet on the right hand side shows another version of the same \textit{compare} method in \textit{WritableComparator} class but it is extracted from the latest version of \texttt{hadoop}. We can obviously see that they are highly similar except one line, \verb|buffer.reset(null,0,0);|, is added in the latest version after \verb|key2.readFields(buffer);|. The added line is intended for cleaning up the reference in \verb|buffer| variable. While this change has already been introduced into \textit{compare} method in the latest version of \texttt{hadoop}, the code example in Stack Overflow post is still unchanged. This example shows that there can be inconsistencies between online code clones and its original. The code snippet on Stack Overflow can be outdated.  %Since reusing source code from Stack Overflow is considered a common practice nowadays, the scale of online code cloning is more than intra or inter project clone in a local code bases. 
%This is an emerging and challenging problem. Since studies in this area are still limited, we aim to gain more insight of the problem in this study. %We are interested to gain more insights of online code clone in this study.

@@

\vspace{0.5ex}%
\noindent\textbf{1.~A manual study of online code clones:} 
We used two clone detection tools to discover 315,786,118 similar code snippet pairs and manually investigated 3,595 candidate clone pairs between Java code snippets obtained from Stack Overflow accepted answers and 111 Java open source projects.

\vspace{0.5ex}%
\noindent\textbf{2.~Addressing the problems of outdated and license-violating online clones on Stack Overflow:} Our study shows that there are at least 523 clones that have been obviously copied from open source projects or external online sources to Stack Overflow as code examples which potentially violate their software licenses. Importantly, 53 out of the 96 online code clones on Stack Overflow are outdated and questionable for being reused.

\vspace{0.5ex}%
\noindent\textbf{3.~Online code clone oracle:} The 3,595 manually investigated and validated online clone pairs are available for download on the study website\footnote{https://some.where} and can be used as a clone oracle.

@@

\textbf{Open source systems}: we selected an established corpus for an empirical software engineering study called \textbf{Qualitas} \cite{QualitasCorpus} for this study. It is a curated Java corpus that has been used in several software engineering studies \cite{Taube-Schock2011,Beckman2011,Vasilescu2011,Omar2012}. The projects in the corpus represent various domains of software systems ranging from programming language to 3D and visualisation \cite{QualitasCorpus}. We selected the 20130901r release of Qualitas corpus containing 112 Java open source projects. This release contains projects with releases no later than 1st September 2013. We chose a snapshot late back in 2013 since we are interested in online code clones in the direction from open source projects to Stack Overflow. The 20130901r snapshot provides Java code that is at least 3 years old from the time of the experiment (January to December 2016). The time difference is sufficiently long for a number of code snippets to be copied onto Stack Overflow. Out of 112 Qualitas projects, there is one project, \texttt{jre}, that does not contain Java source code due to its licensing limitation \cite{QualitasCorpus} so it is removed from the study. This resulted in total of 111 projects analysed in the study. As shown in \Cref{tab:datasets}, the 111 Qualitas project have 160,937 Java files containing 19,086,883 lines of code. %Details of the 109 Qualitas projects and their licenses are listed in Table \ref{t:new_and_old}.

@@

\begin{table}
	\centering
	\caption{Statistics of clones found between Stack Overflow and Qualitas projects using Simian (\textit{S}) and NiCad (\textit{N}) with default (\textit{D}) and EvaClone (\textit{E}) configurations \FIXME{boxplots here?}}
	\label{tab:raw_stats}
	\small
	\resizebox{\columnwidth}{!}{%
		\begin{tabular}{l|r|r|r|r}
			\hline
			Stats & \multicolumn{1}{c|}{$S_D$} & \multicolumn{1}{c|}{$S_E$} & \multicolumn{1}{c|}{$N_D$} & \multicolumn{1}{c}{$N_E$} \\
			\hline
			Snippets & 1,086 & 1,531 & 1,392 & 12,886 \\
			Total C$_{\textrm{\textit{pairs}}}$ & 67,570 & 63,635,844 & 632,855 & 251,449,849 \\
			Avg.~C$_{\textrm{\textit{pairs}}}$ & 62 & 41,565 & 455 & 19,356 \\
			Avg.~C$_{\textrm{\textit{size}}}$ & 7.72 & 4.79 & 9.84 & 5.33 \\
			Avg.~C$_{\textrm{\textit{\%}}}$ & 29\% & 28\% & 25\% & 21\% \\
			\hline
		\end{tabular} %
	}
\end{table}

@@

Agreed clone pairs are clone pairs that pass Bellon's good- or ok-match criteria and selected for manual investigation. Similar to the original study, we select a threshold \textit{p} of 0.7 for both \textit{good} and \textit{ok} pairs \cite{Bellon2007}. %The number of projects processed by the clone detection tools are listed in \Cref{tab:projects_missing}. 
We encountered NiCad failures with a few Qualitas projects.~$N_D$ could not detect clones in \texttt{hibernate} due to clustering errors. $N_E$ generated renaming errors for 5 projects including \texttt{vuze}, \texttt{hibernate}, \texttt{myfaces}, \texttt{netbeans}, and \texttt{spring}. We had contacted the creator of NiCad regarding the issues. They identified them as problems of long file paths and TXL grammars which will be fixed in the next NiCad releases. As a result, we did not have NiCad clones from these projects in the agreed clone pairs. Simian clones of the same projects also disappeared from the agreed clone pairs since they could not find matches.

@@

\textbf{To answer RQ1, we found 32,039 clone candidates between 111 Qualitas projects and 144,075 Stack Overflow snippets. They are 2,308 \textit{good}, 11,749 \textit{ok}, 17,801 $S_D$, and 181 $N_D$ pairs. After classification, we found at least \FIXME{NUMBER} online code clones pairs between Stack Overflow and Qualitas.}

@@

\begin{table}
	\centering
	\caption{Seven patterns of online code cloning}
	\label{tab:classification_scheme}
	\resizebox{\columnwidth}{!}{%
		\begin{tabular}{c|p{8.4cm}}
			\hline 
			Patt. & Descriptions \\ 
			\hline 
			QS & Cloned from Qualitas project to Stack Overflow (Q $\rightarrow$ S). \\ 
			\hline 
			SQ &Cloned from Stack Overflow to Qualitas project (S $\rightarrow$ Q). \\ 
			\hline 
			UD & Cloned from each other or from an external source \textit{X} outside the project (unknown) (S $\leftrightarrow$ Q $\vee$ (X $\rightarrow$ S $\wedge$ X $\rightarrow$ Q)).
			\\ 
			\hline 
			ES & Cloned from an external source (X $\rightarrow$ S $\wedge$ X $\rightarrow$ Q).
			\\ 
			\hline 
			BP & Boiler-plate or IDE auto-generated
			\\ 
			\hline 
			IN & Inheritance, interface implementation 
			\\ 
			\hline 
			FC & Accidental similarity, false clones \\ 
			\hline 
		\end{tabular}  %
	}
\end{table}

@@

Nevertheless, we adopted one of Kapser's cloning patterns, boiler-plate code and API/library protocol as pattern BP. We then added 6 new patterns observed as common cloning patterns from our preliminary study. The seven patterns include QS, SQ, UN, ES, BP, IN, and FC as presented in \Cref{tab:classification_scheme}. QS (\textbf{Q}ualitas to \textbf{S}tack Overflow) represents clones that has evidence to be copied from Qualitas to Stack Overflow (by having comments in source code and explanation/links in Stack Overflow post). Pattern SQ (\textbf{S}tack Overflow to \textbf{Q}ualitas) is the opposite of QS. UD (\textbf{U}nknown \textbf{D}irection) is cloning that creates exactly identical or highly similar clones but without any attribution of copying. They are unique enough not be boiler-plate and inheritance or interface implementation. ES (\textbf{E}xternal \textbf{S}ources) is a cloning that has an evidence of copying from an external source(s). Pattern BP (\textbf{B}oiler-\textbf{P}late) represents clones containing boiler-plate code of \verb|equals()| methods, getters and setters, or IDE-generated code (e.g.~GUI components). Pattern IN (\textbf{In}heritance/Interface) is cloning because of inheritance of the same super class or implementation of the same interface. They usually share similar overriding methods. The last pattern, FC (\textbf{F}alse \textbf{C}lones), represents false clone pairs. They can be either accidentally similar clones (e.g.~similar \texttt{try-catch} statements), similar clones after code normalisation, or just false positives of the tools. Using the classification patterns, we can also calculate the number of true and false positives. We are looking for unique and meaningful clones in this study. Thus, we consider clone pairs classified into pattern QS, SQ, and UN as true positive, and BP, IN, and FC as false positive.

@@

\textbf{To answer RQ2, we found that ...}

@@

\Cref{fig:outdated} shows the findings of outdated online clones on Stack Overflow. The comparison with the clones' latest versions revealed that 55 clone pairs were outdated and they were all Stack Overflow accepted answers. \texttt{hadoop} and Spring have the maximum number of 9 outdated code clones, followed by 6 from Tomcat, and 5 from \texttt{eclipse-SDK}. An example of outdated code in \texttt{hadoop}'s \textit{WritableComparator.java} is shown in \Cref{fig:before-after} as we discussed before. We also found a few outdated code which contained heavy modifications. For example, the code snippet in Stack Overflow post 23520731, a copy of \textit{SchemaUpdate.java} in \texttt{hibernate}, it had been heavily modified in the latest version (as shown in \Cref{fig:hibernate_outdated_code}). Lastly, we found some ``orphan'' snippets. These snippets cannot find their originals in the latest version of the projects anymore. For example, the snippet in Stack Overflow post 3758110, a copy of \textit{DefaultAnnotationHandlerMapping.java} in \texttt{spring}, was deleted in commit \texttt{02a4473c62d8240837bec297f0a1f3cb67ef8a7b} by Chris Beams on 20th January 2012 at 22:51:02, two years after it was posted. %The latest version of Spring does not contain the file anymore.

The outdated online code clones can cause problems ranging from uncompilable code due to different API usage to bug propagations. An outdated code with a subtle change (e.g.~\Cref{fig:before-after}) may be copied and reused without awareness from developers. Although Stack Overflow has a voting mechanism that may mitigate this outdated code issue, the check mark symbol in front of the accepted answer is still attractive to naive developers who are ignorant.

\textbf{For RQ3, we found 55 code snippets on Stack Overflow that are outdated and questionable for being reused.}
%Usually when developers reuse a code snippet from a Stack Overflow post and find that it does not work nor compatible with their environment. They can cast a down vote to that answer resulting in low votes for the answer (which might be outdated). However, if the answer is marked as accepted by the person who asks the question, the check mark symbol attached to the answer is still attractive to naive developers who are ignorant.

@@

	\begin{tabular}{r|l|c|p{4.5cm}|r|r|l|l|l|c|l}

@@

		No. & Project & Ver. & File & Start & End & License & SO Post & License & $C$ & C$_{\textit{\textrm{date}}}$ \\

@@

			1 & \texttt{aspectj} & 1.6.9  & aspectjtools/../Agent.java  & 7 & 18 & -- & 18303692 & -- & $M$  & 2015-09-08 \\
			2 & \texttt{aspectj} & 1.6.9  & aspectjweaver/../Agent.java  & 7 & 18 & -- & 18303692 & & $M$  & 2015-09-08 \\
			3 & \texttt{eclipse-SDK} & & GenerateToStringAction.java  & 113 & 166 & EPLv1 & 2513183 & EPLv1 & $M$  &  2015-03-17 \\
			4 & \texttt{eclipse-SDK} & & GenerateToStringAction.java  & 117 & 126 & EPLv1  &  2513183	& EPLv1 & $M$  &  2015-03-17 \\
			5 & \texttt{eclipse-SDK} & & GenerateToStringAction.java  & 143 & 165 & EPLv1  &  2513183	& EPLv1 & $M$  &  2015-03-17 \\
			6 & \texttt{eclipse-SDK} & & GenerateToStringAction.java  & 178 & 187 & EPLv1  &  2513183	& EPLv1 & $M$  & 2011-03-01 \\
			7 & \texttt{eclipse-SDK} & & WizardDialog.java  & 377 & 394 & EPLv1  &   11861598	& -- & $M$  &  2011-02-03 \\
			8 & \texttt{hadoop} & 1.0.0 & DBCountPageView.java  & 275 & 287 & Apache-2 & 21702608 & -- & $M$  & 2011-06-12 \\
			9 & \texttt{hadoop} & 1.0.0 & DBCountPageView.java  & 289 & 309 & Apache-2 & 21702608 & -- & $M$  & 2011-06-12 \\
			10 & \texttt{hadoop} & 1.0.0 & JobSubmissionFiles.java  & 46 & 55 & Apache-2 & 14845581 & -- & $M$  & 2012-06-25 \\
			11 & \texttt{hadoop} & 1.0.0 & mapred/../LineRecordReader.java  & 47 & 60 & Apache-2 & 16180910 & -- & $M$  & 2011-07-25 \\
			12 & \texttt{hadoop} & 1.0.0 & mapreduce/../LineRecordReader.java  & 75 & 99 & Apache-2 & 16180910 & -- & $M$  & 2011-07-25 \\
			13 & \texttt{hadoop} & 1.0.0 & StringUtils.java  & 40 & 56 & Apache-2 & 801987 & -- & $M$  & 2013-02-04 \\
			14 & \texttt{hadoop} & 1.0.0 & TestJobCounters.java  & 186 & 192 & Apache-2 & 18833798 & -- & $M$  & 2011-06-12 \\
			15 & \texttt{hadoop} & 1.0.0 & TextOutputFormat.java  & 75 & 99 & Apache-2 & 16928749 & -- & $M$  & 2011-06-12 \\
			16 & \texttt{hadoop} & 1.0.0 & WritableComparator.java  & 44 & 54 & Apache-2 & 22315734 & -- & $M$  & 2014-11-20 \\
			17 & \texttt{hibernate} & 4.2.2 & ConnectionProviderInitiator.java  & 65 & 93 & -- & 15168494 & -- & $M$  & 2012-06-24 \\
			18 & \texttt{hibernate} & 4.2.2 & Example.java  & 224 & 243 & -- & 24924255 & -- & $M$  & 2013-04-23 \\
			19 & \texttt{hibernate} & 4.2.2 & SchemaUpdate.java  & 115 & 168 & -- & 23520731 & -- & $M$  & 2016-02-05 \\
			20 & \texttt{hibernate} & 4.2.2 & SettingsFactory.java  & 244 & 255 & -- & 8257554 & -- & $D$  & 2011-03-11 \\
			21 & \texttt{hibernate} & 4.2.2 & SQLServer2005LimitHandler.java  & 43 & 61 & -- & 23967852 & -- & $M$  & 2015-03-12 \\
			22 & \texttt{jasperreports} & 3.7.4 & JRVerifier.java  & 982 & 998 & LGPLv3+ & 8037824 & -- & $M$  & 2008-04-17 \\
			23 & \texttt{jasperreports} & 3.7.4 & JRVerifier.java  & 1221 & 1240 & LGPLv3+ & 8037824 & -- & $M$  & 2011-05-20 \\
			24 & \texttt{jfreechart} & 1.0.13 & AbstractXYItemRenderer.java  & 532 & 569 & LGPLv2.1+ & 12936580 & -- & $M$  & 2016-02-19 \\
			25 & \texttt{jfreechart} & 1.0.13 & KeyToGroupMap.java  & 18 & 30 & LGPLv2.1+ & 16058183 & -- & $M$  & 2013-07-03 \\
			26 & \texttt{jfreechart} & 1.0.13 & SpiderWebPlot.java  & 502 & 520 & LGPLv2.1+ & 21998949 & -- & $M$  & 2008-06-02 \\
			27 & \texttt{jfreechart} & 1.0.13 & SpiderWebPlot.java  & 522 & 536 & LGPLv2.1+ & 21998949 & -- & $M$  & 2008-06-02 \\
			28 & \texttt{jgraph} & 5.13.0.0 & HelloWorld.java  & 16 & 22 & LGPLv2.1+ & 6722760 & -- & $R$  & 2014-04-13 \\
			29 & \texttt{jgraph} & 5.13.0.0 & HelloWorld.java  & 28 & 40 & LGPLv2.1+ & 6722760 & -- & $R$  & 2014-04-13 \\
			30 & \texttt{jgraph} & 5.13.0.0 & HelloWorld.java  & 31 & 36 & LGPLv2.1+ & 6722760 & -- & $R$  & 2014-04-13 \\
			31 & \texttt{jgraph} & 5.13.0.0 & HelloWorld.java  & 39 & 56 & LGPLv2.1+ & 6722760 & -- & $R$  & 2014-04-13 \\
			32 & \texttt{jstock} & 1.0.7c & GoogleMail.java  & 18 & 42 & GPLv2+ & 14940863 & -- & $M$  & 2015-12-13 \\
			33 & \texttt{jstock} & 1.0.7c & GoogleMail.java  & 18 & 42 & GPLv2+ & 24680923 & -- & $M$  & 2015-12-13 \\
			34 & \texttt{jung2} & 2\_0\_1  & ShortestPathDemo.java  & 106 & 117 & -- & 6025026 & -- & $M$  & 2010-04-13 \\
			35 & \texttt{jung2} & 2\_0\_1  & ShortestPathDemo.java  & 158 & 172 & -- & 6025026 & -- & $M$  & 2010-04-13 \\
			36 & \texttt{junit} & 4.11 & Assert.java  & 33 & 52 & -- & 23586872 & -- & $M$  & 2015-05-12 \\
